\thesistitle

### 2019-07-25 sections/background.tex
Refactoring background

\section{Refactoring methods}
Martin Fowler recently released the second edition of his Refactoring book \cite{fowler2018refactoring}. This book has been updated to the modern state of software engineering. The sentence in which he stresses the importance of unifying duplication in source code remains present in both books \cite{fowler1999refactoring, fowler2018refactoring}.

The main method for dealing with duplication in source code, as described by Martin Fowler, is to extract the duplication to a common place. In most IDE's this refactoring method is called ``Extract Method''.

\subsection{Extract Method}
Method extraction is one of the most used methods of refactoring duplication in source code. Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}. Method extraction can move matching functionality between methods to a common place: a new method. An example of this procedure is displayed in figure \cite{fig:extractmethod}.

>>>>

\section{Refactoring methods}
Martin Fowler recently released the second edition of his Refactoring book \cite{fowler2018refactoring}. In this book he exclaims that \textit{``if you see the same code structure in more than one place, you can be sure that your program will be better if you find a way to unify them''} \cite{fowler1999refactoring, fowler2018refactoring}. He describes several methods to deal with duplication, dependent on the context of the clone. In this section we describe the methods which we use in this study.

\subsection{Extract Method}
The main method for dealing with duplication in source code, as described by Martin Fowler, is to extract the duplication to a common place. This refactoring method is called ``Extract Method''. Several studies have already concluded that most duplication in source code is found in the body of methods \cite{lozano2007evaluating, white2016deep, bergman2004ethnographic}. Method extraction can move matching functionality in method bodies to a common place, namely a new method. An example of this procedure is displayed in figure \cite{fig:extractmethod}.
